INTELLIGENT SYSTEMS

### 2021-04-01 slides.tex
start experiments slide paper3

\documentclass[10pt]{beamer}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{bibentry}
\usepackage{biblatex}
\usepackage{adjustbox}
\usepackage[font=scriptsize]{caption}
\usepackage{subcaption}
\captionsetup[figure]{labelsep=period}
\captionsetup[subfigure]{labelformat=simple} % default is 'parens'
\renewcommand\thesubfigure{\thefigure.\alph{subfigure}.}

@@

>>>>

\documentclass[10pt]{beamer}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{bibentry}
\usepackage{biblatex}
\usepackage{adjustbox}
\usepackage[font=scriptsize]{caption}
\usepackage{subcaption}
\captionsetup[figure]{labelsep=period}
\captionsetup[subfigure]{labelformat=simple} % default is 'parens'
\renewcommand\thesubfigure{\thefigure.\alph{subfigure}.}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}

@@

\begin{frame}{THE PROPOSED COMPRESSION FRAMEWORK pt1}
    The proposed system is composed of two convolutional neural networks:
    \begin{enumerate}
        \item \emph{ComCNN}: used for compact representation of images
        \item \emph{RecCNN}: used for decoding and reconstruction of images
    \end{enumerate}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8 \linewidth]{images/paper3/framework.png}
        \centering
        \caption{Up: the ComCNN. Down: the RecCNN. Right: the codec.}
        \label{fig: framework}
    \end{figure}
\end{frame}

\begin{frame}{THE PROPOSED COMPRESSION FRAMEWORK pt2}
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[H]
                \includegraphics[width = 1 \linewidth]{images/paper3/ComCNN.png}
                \caption{ComCNN architecture.}
            \end{figure}
            \begin{block}{Parameter optimizations}
                \small $$ \hat{\theta_1} = \argmin\limits_{\theta_1}||Re(\hat{\theta_2},Cr(\theta_1,x))-x||^2 $$
            \end{block}
            \begin{block}{Loss Function}
               \tiny $$ L_1(\theta_1) = \frac{1}{2N}\sum_{k=1}^N||Re(\hat{\theta_2}, C_r(\theta1,x_k))-x_k||^2 $$
            \end{block}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[htbp]
                \centering
                \includegraphics[width = 1 \linewidth]{images/paper3/RecCNN.png}
                \centering
                \caption{RecCNN architecture.}
            \end{figure}
            \begin{block}{Parameter optimizations}
                \small $$ \hat{\theta_2} = \argmin\limits_{\theta_2}||Re(\hat{\theta_2},\hat{x}_m)-x||^2 $$
            \end{block}
            \begin{block}{Loss Function}
                \tiny $$ L_2(\theta_2) = \frac{1}{2N}\sum_{k=1}^N||res(Co(\hat{x}_{mk}), \theta_2) - (Co(\hat{x}_{mk})-x_k)||^2 $$
             \end{block}
        \end{minipage}
    \end{minipage}
\end{frame}

\begin{frame}{EXPERIMENTS}
